---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# SELINA

<!-- badges: start -->
<!-- badges: end -->

SELINA is a deep learning-based framework for single cell assignment with multiple references. The algorithm consists of three main steps: cell type balancing, pre-training and fine-tuning. The rare cell types in reference data are first oversampled using SMOTE(Synthetic Minority Oversampling Technique), and then the reference data is trained with a supervised deep learning framework using MADA(Multi-Adversarial Domain Adaptation). An autoencoder is subsquently used to fine-tune the parameters of the pre-trained model. Finally, the labels from reference data are transferred to the query data based on the fully-trained model. Along with the annotation algorithm, we also collect 136 datasets which were uniformly processed and curated to provide users with comprehensive pre-trained models.

## Installation

You can install the released version of SELINA from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("SELINA")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("SELINA-team/SELINA.R")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(SELINA)
## basic example code
```
